Pleiotropic expression quantitative trait loci are located in cis-regulatory modules, closer to more target genes and with smaller effects on the genes

### 2023-05-04 doc/presentation_230511_centuriday2023/presentation_centuri2023_marseille.tex
DOC

\newcommand*{\presentationgoldparispath}{../presentation_230120_gold2022_paris/fig/}%

@@

\begin{itemize}
\item Quantitative trait loci (QTL) are variants associated with changes of quantitative phenotypes
\item Expression (eQTL) are variants associated with changes of gene expression in a given tissue
\item eQTLs provide a putative molecular mechanism of a variant
\end{itemize}
%
\vfill
%
What are the properties of pleiotropic eQTLs?

\includegraphics[width=\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4a.jpg}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Approach}

\begin{enumerate}
\item Compute colocalization of eQTLs and GWAS variants
\item Split eQTLs by the number of associated disease categories
\item Compare properties of pleiotropic eQTLs
\end{enumerate}
%
\vfill
%
What are the properties of pleiotropic eQTLs?

\includegraphics[width=\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4a.jpg}

@@

>>>>

\newcommand*{\presentationgoldparispath}{../presentation_230120_gold2022_paris/fig/}%
\newcommand*{\mspath}{../../out/gwas417/pval_5e-08/r2_0.1/kb_1000/window_1000000/75_50}%

@@

        \begin{itemize}
            \item Quantitative trait loci (QTL) are variants associated with changes of quantitative phenotypes
            \item Expression (eQTL) are variants associated with changes of gene expression in a given tissue
            \item eQTLs provide a putative molecular mechanism of a variant
        \end{itemize}
        \vfill
        What are the properties of pleiotropic eQTLs?

        \includegraphics[width=0.7\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4a.jpg}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Annotation of eQTLs traits using colocalization analysis}

        \begin{center}
            \includegraphics[width=0.6\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4bc.png}
        \end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Strategy}

        \begin{enumerate}
            \item Compute colocalization of eQTLs and GWAS variants
            \item Split eQTLs by the number of associated disease categories
            \item Compare molecular properties of pleiotropic eQTLs
        \end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic variants associated to more eQTL genes?}

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        \end{center}
